---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/gen_contents.R")
```

# Contents, figures and tables {.unnumbered}

## Contents of the report

This web book version of the report is structured into 17 chapters and two
appendices.

:::{.custom-toc .report-contents}

```{r, list-sections}
#| output: asis
cat(get_content_list("sec", max_depth = 1), sep = "\n")
```

:::

### Changes compared to the original 2019 publication

Please note that @sec-country-profiles of this web book provides an
interactive version of the report content which may not be fully accessible,
[static versions](Z_00_country_profiles_old.qmd) of the country profiles are
available in the Appendices to this report.

## List of figures

:::{.custom-toc .list-of-figures}

```{r, list-figures}
#| output: asis
cat(get_content_list("fig", insert_breaks = FALSE), sep = "\n")
```

:::

## List of tables

:::{.custom-toc .list-of-tables}

```{r, list-tables}
#| output: asis
cat(get_content_list("tbl"), sep = "\n")
```

:::

