---
execute:
  echo: false
---

```{r, setup}
#| output: false
source("R/gen_contents.R")
```

# Contents {.unnumbered}

# Contents, figures and tables {.unnumbered}

## Contents of the report

This web book version of the report is structured into 17 chapters and two
appendices.

:::{.custom-toc .report-contents}

```{r, list-sections}
#| output: asis
cat(get_content_list("sec"), sep = "\n")
```

:::

### Changes compared to the original 2019 publication

The [country profiles](04_00_country_profiles.qmd) part of this web book were
presented as a single chapter (Chapter 4) in the original 2019 publication. For
improved navigation and readability this part of the report has been split into
separate chapters. Footnotes have been added to charts, tables and chapters to
indicate the resulting differences in numbering between this web book and the
original 2019 publication.

## List of figures

:::{.custom-toc .list-of-figures}

```{r, list-figures}
#| output: asis
cat(get_content_list("fig", insert_breaks = FALSE), sep = "\n")
```

:::

## List of tables

:::{.custom-toc .list-of-tables}

```{r, list-tables}
#| output: asis
cat(get_content_list("tbl"), sep = "\n")
```

:::

