---
execute:
  echo: false
---

```{r, setup}
#| output: false

source("R/tbl_helpers.R")
source("R/references.R")

tbl_data_sources <- readr::read_csv("tables/data_sources.csv")

```

# InCiSE 2019 data sources {#sec-data-sources}

The InCiSE Index brings together a large number of separate data sources
measuring civil service or public sector effectiveness. Readers are free to
copy and reuse the InCiSE Index, indicator and metric scores. Reuse of the
original data is subject to the intellectual property rights of third parties.
Please refer to the corresponding organisation's websites and data licences to
ensure compliance with their reuse obligations.

This Annex provides a list of all the data sources used to compile the 2019
edition of InCiSE. @tbl-data-sources shows the data sources by indicator. For
more details on the data sources and the construction of the indicators please
refer to the [Technical Report](http://incise-project.github.io/incise2019-techreport/).

```{r}
#| label: tbl-data-sources
#| tbl-cap: Data sources of the InCiSE indicators
#| classes: .no-stripe

out_tbl_body <- tbl_data_sources |>
  dplyr::add_count(indicator, name = "row_count") |>
  dplyr::mutate(
    indicator = dplyr::case_match(
      indicator,
        "CAP" ~ "Capabilities",
        "CRM" ~ "Crisis and risk management",
        "DIG" ~ "Digital services",
        "FFM" ~ "Fiscal and financial management",
        "HRM" ~ "HR management",
        "INC" ~ "Inclusiveness",
        "INT" ~ "Integrity",
        "OPN" ~ "Openness",
        "POL" ~ "Policy making",
        "PRO" ~ "Procurement",
        "REG" ~ "Regulation",
        "TAX" ~ "Tax administration"
    ),
    row_output = dplyr::case_when(
      row_count == 1 ~ 
        paste0("<tr><td>", indicator, "</td><td>", source_ref, "</td></tr>"),
      indicator != dplyr::lag(indicator, default = "") ~ 
        paste0("<tr><td rowspan=\"", 
               row_count, "\">", 
               indicator,
               "</td><td>",
               source_ref, "</td></tr>"),
      TRUE ~ 
        paste0("<tr><td>", source_ref, "</td></tr>")
    )
  )

out_tbl <- c(
  "<table class=\"table table-sm small\">",
  "<thead>",
  "<tr class=\"header gt_col_headings\">",
  "<th class=\"gt_col_heading gt_columns_bottom_border\">Indicator</th>",
  "<th>Data sources</th></tr>",
  "</thead>",
  "<tbody class=\"gt_table_body\">",
  out_tbl_body$row_output,
  "</tbody>",
  "</table>"
)

htmltools::HTML(out_tbl)

```

::: {#data-source-refs .references .hanging-indent}
```{r, ds_refs}
#| output: asis
gen_ds_refs("tables/data_sources.bib")
```
:::
